Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-05-21 article_review2.0/Manuscript.tex
removed extra space in purple comments
Minor changes in Manuscript and reviewers letter

\newcommand{\comment}[1]{{\color{purple} #1 }}
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
\comment{\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{2(n-1)} \sum \limits_{i=0}^{n-1} \left[\left( f(\vx_i) - \widehat{\mu}\right)^2 + \left( f(\vx'_i) - \widehat{\mu}\right)^2\right],
 \end{equation}
with
\begin{equation}
\widehat{\mu} =  \frac{1}{2n} \sum \limits_{i=0}^{n-1} \left[ f(\vx_i)+f(\vx'_i)\right].
\label{mu.est}
\end{equation}}

>>>>

\newcommand{\comment}[1]{{\color{purple} #1}}
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
\begin{equation}\label{mu.est}
\widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left(f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1}f(\vx_i).
\end{equation}
\comment{Equation \eqref{mu.est} can be improved if we use the $2n$ evaluations $f(\vx_i)$ and $f(\vx'_i)$. While this would be an important improvement to estimate the indices' denominator, the error construction described in Section \ref{sec:3} would require additional computations. Because of the new computations in the algorithm, the additional benefit of using $2n$ evaluations could become more costly than beneficial.}

### 2017-05-21 article_review2.0/reviewer_letter.tex
Minor changes in Manuscript and reviewers letter

\textcolor{blue}{
\begin{itemize}
\item[*]Points $1$, $2$, $3$, $4$ and $7$ have all been addressed accordingly.
\item[*]Concerning point $5$, we indeed intended to say that ``the 3d coordinates are independent but not that the points themselves''. As such, we have followed the suggested correction and removed the $iid$ mention.
\item[*]Concerning point $6$, we simply missed this correction during the first review. We thank the reviewer for catching it.
\end{itemize}}

@@

\textcolor{blue}{
\begin{itemize}
\item[*]Points $1$, $5$, $6$, $7$, $9$, $10$, $11$ and $12$ have all been addressed accordingly.
\item[*]Concerning point $2$, $\sigma^2$ (along with $\mu$) has been rewritten to use all $2n$ observations.
\item[*]Concerning point $3$, `we generalized' has been replaced by `we use the generalization from' to answer the issue.
\item[*]Concerning point $4$, we decided to keep the modification in the definition to stress that bad point sets are ruled out.
\item[*]Concerning point $8$, further explainations were added on the new g-function (inspired from the reviewer's comments on the first review).
\end{itemize}}

>>>>

\textcolor{blue}{
\begin{itemize}
\item[*]Points $1$, $2$, $3$, $4$ and $7$ have all been addressed accordingly.
\item[*]Concerning point $5$, we intended to mention Owen's estimator in its original form, designed with uniform iid points. Since it uses iid uniform points, the integral (or expected value to be estimated) is defined over the uniform measure. Hence, because the integral is defined over the uniform measure, we can apply quasi-Monte Carlo points instead of uniform iid points. This does not imply that the quasi-Monte Carlo points need to be independent. As the reviewer mentions, since this is confusing, we have followed the suggested correction and removed the $iid$ mention.
\item[*]Concerning point $6$, we simply missed this correction during the first review. We thank the reviewer for catching it.
\end{itemize}}

@@

\textcolor{blue}{
\begin{itemize}
\item[*]Points $1$, $5$, $6$, $7$, $9$, $10$, $11$ and $12$ have all been addressed accordingly.
\item[*]Concerning point $2$, although this is a great idea, this is not as convenient if we use the error estimation from Section 3. We could proceed by estimating $\mu$ (the same method for $\sigma^2$) with $f(\vx_i)$ and computing the error bound, estimating $\mu$ with $f(\vx'_i)$ and computing the error bound. Then, if $\mu\in[a,b]$ and $\mu'\in[a',b']$, the new estimator would be the mid point in $[a,b]\cap[a',b']$. This would require including the computation of the fast Fourier transform for the $f(\vx'_i)$ evaluations which could be too costly for the benefits it provides (given that the hard integral is in the numerator). As the reviewer suggests, it is important to consider that we have the $f(\vx'_i)$ evaluations and this could always be used. We added a comment after equation (7) explaining this point.
\item[*]Concerning point $3$, `we generalized' has been replaced by `we use the generalization from' to answer the issue.
\item[*]Concerning point $4$, we decided to keep the modification in the definition to stress that bad point sets are ruled out.
\item[*]Concerning point $8$, further explainations were added on the new g-function (inspired from the reviewer's comments on the first review).
\end{itemize}}
